---
title: "Broadband Measurements"
author: "Jaewon R. Choi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.align = 'center', warning = FALSE, message = FALSE)
```

Here I will explore different broadband measurements available. In the current dataset, we have four different measures of broadband:

* **FCC Broadband Availability**: % of people per county with access to fixed terrestrial broadband at speeds of 25 Mbps / 3 Mbps as of the end of 2017
* **Microsoft Broadband Usage**: % of people per county that use the Internet at broadband speeds based on people's usage of Microsoft services as of November 2019
* **ACS Broadband Subscription**: % of people per county that has broadband subscriptions of any type (2018 ACS 5-year estimates)
* **M-Lab Broadband Usage**: Average % of people who reported broadband speed of 25 Mbps / 3 Mbps in M-Lab tests from September 2019 to December 2019

Throughout this page, I will explore descriptive statistics of these measures, distributions of the measures, correlations between these measures, and also how these measures look like on the map geographically.

## Descriptive Statistics of Broadband Measures

```{r Impoart Libraries, results='hide'}
library(leaflet)
library(tidyverse)
library(RColorBrewer)
library(tigris)
library(ggplot2)
library(sp)
library(stargazer)
library(gridExtra)

#### Import the merged dataset V2 ####
tx_bb_entrepreneur_merged_v2 <- read.csv("https://raw.githubusercontent.com/jwroycechoi/broadband-entrepreneurship/master/Datasets/Broadband-Entrepreneurship-TX-merged_v2.csv")
tx_bb_entrepreneur_merged_v2 <- tx_bb_entrepreneur_merged_v2 %>% 
  mutate(pct_fixed_acs_2018 = pct_fixed_acs_2018/100)
## Set up spatial dataframe
tx_county <- counties("Texas")
tx_bb_entrepreneur_merged_v3 <- sp::merge(tx_county, tx_bb_entrepreneur_merged_v2,
                                          by.x = "GEOID", by.y = "FIPS")
```

```{r Descriptive Statistics, results='asis'}
#### Descriptive Statistics ####
tx_bb_entrepreneur_merged_v2 %>% 
  select(pct_broadband_FCC, pct_broadband_MS, pct_fixed_acs_2018, pct_broadband_mlab) %>% 
  stargazer(as.data.frame(.), title = "Descriptive Stats of Broadband Measures",
            column.labels = c("FCC","MS","ACS Fixed","M-Lab"),type = "html")
```

## Distributions of Broadband Measures

```{r Distributions of Broadband Measures, echo=FALSE, cache=TRUE, message=FALSE}
grid.arrange(
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_FCC)) + geom_histogram() + theme_minimal() + xlab("FCC Broadband") + ylab("Frequency") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_MS)) + geom_histogram() + theme_minimal() + xlab("MS Broadband") + ylab("Frequency") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_fixed_acs_2018)) + geom_histogram() + theme_minimal() + xlab("ACS Broadband Subscription") + ylab("Frequency") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty(),
                       limits = c(0,1)),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_mlab)) + geom_histogram() + theme_minimal() + xlab("M-Lab Broadband") + ylab("Frequency") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty(),
                       limits = c(0,1)),
  nrow = 2, ncol = 2, top = grid::textGrob("Broadband Measure Distribution", gp = grid::gpar(fontface="bold",fontsize=14))
)
```

## Correlations b/w Broadband Measures

```{r Correlations b/w Broadband Measures, echo=FALSE, cache=TRUE, message=FALSE}
grid.arrange(
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_FCC, y = pct_broadband_MS)) + 
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() + 
    theme(axis.text = element_text(size = 11)) +
    labs(x = "FCC Broadband", y = "Microsoft Broadband") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_FCC, y = pct_fixed_acs_2018)) +
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() +
    theme(axis.text = element_text(size = 11)) +
    labs(x = "FCC Broadband", y = "ACS Fixed BB Subscription") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_FCC, y = pct_broadband_mlab)) +
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() + 
    labs(y = "M-Lab Broadband", x = "FCC Broadband") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_MS, y = pct_broadband_mlab)) + 
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() + 
    labs(x = "Microsoft Broadband", y = "M-Lab Broadband") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_broadband_MS, y = pct_fixed_acs_2018)) + 
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() +
    labs(x = "Microsoft Broadband", y = "ACS Fixed BB Subscription") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  ggplot(tx_bb_entrepreneur_merged_v2, aes(x = pct_fixed_acs_2018, y = pct_broadband_mlab)) +
    geom_point(color = "grey10", alpha = 0.7, size = 3) + 
    geom_smooth(method = "lm", color = "darkorange3") + theme_minimal() +
    labs(x = "ACS Fixed BB Subscription", y = "M-Lab Broadband") +
    scale_x_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    scale_y_continuous(labels = scales::percent, breaks = scales::breaks_pretty()) +
    ggpubr::stat_cor(p.accuracy = 0.001, r.accuracy = 0.01),
  nrow = 2, ncol = 3, top = grid::textGrob("Correlations b/w Broadband Measures",
                                             gp = grid::gpar(fontface="bold",fontsize=14))
  )

```

## Mapping Different Broadband Measures

```{r Map Setup, echo=FALSE, results='hide', cache=TRUE}
## Create continuous color palette function based on FCC broadband range (0~1) ##
pal <- colorNumeric(palette = "YlOrRd", domain = tx_bb_entrepreneur_merged_v2$pct_broadband_FCC)
## Set a popup template ##
popup_tx <- paste0("<strong>", tx_bb_entrepreneur_merged_v3$county,
                   "</strong><br />FCC: ", tx_bb_entrepreneur_merged_v3$pct_broadband_FCC*100, "%",
                   "<br />MS: ", tx_bb_entrepreneur_merged_v3$pct_broadband_MS*100, "%",
                   "<br />ACS: ", tx_bb_entrepreneur_merged_v3$pct_fixed_acs_2018*100, "%",
                   "<br />M-Lab: ", round(tx_bb_entrepreneur_merged_v3$pct_broadband_mlab*100, digits = 1), "%")
head(popup_tx)
## Create a map object ##
map <- leaflet(tx_bb_entrepreneur_merged_v3)
```

### FCC Broadband Availability in Texas

```{r FCC Broadband Map, echo=FALSE, cache=TRUE}
## FCC Broadband Map ##
map %>% addTiles() %>% setView(lng = -100.000, lat = 31.000, zoom = 6) %>% 
  addPolygons(stroke = F, smoothFactor = 0.2, fillOpacity = 0.9,
                                   color = ~pal(pct_broadband_FCC),
              popup = ~popup_tx) %>% 
  addLegend("bottomright", pal = pal, values = ~pct_broadband_FCC,
            title = "FCC Broadband (%)",
            labFormat = labelFormat(suffix = "%", transform = function(x) 100*x), na.label = "N/A", opacity = 1)
```

### Microsoft Broadband Usage in Texas

```{r MS Broadband Usage, echo=FALSE, cache=TRUE}
## MS Broadband Map ##
map %>% addTiles() %>% setView(lng = -100.000, lat = 31.000, zoom = 6) %>% 
  addPolygons(stroke = F, smoothFactor = 0.2, fillOpacity = 0.9,
              color = ~pal(pct_broadband_MS),
              popup = ~popup_tx) %>% 
  addLegend("bottomright", pal = pal, values = ~pct_broadband_MS,
            title = "MS Broadband (%)",
            labFormat = labelFormat(suffix = "%", transform = function(x) 100*x), na.label = "N/A", opacity = 1)
```

### ACS Broadband Subscription in Texas

```{r ACS Broadband Subscription, echo=FALSE, cache=TRUE}
## ACS Broadband Subscription Map ##
map %>% addTiles() %>% setView(lng = -100.000, lat = 31.000, zoom = 6) %>% 
  addPolygons(stroke = F, smoothFactor = 0.2, fillOpacity = 0.9,
              color = ~pal(pct_fixed_acs_2018),
              popup = ~popup_tx) %>% 
  addLegend("bottomright", pal = pal, values = ~pct_fixed_acs_2018,
            title = "ACS Broadband Subscription (%)",
            labFormat = labelFormat(suffix = "%", transform = function(x) 100*x), na.label = "N/A", opacity = 1)
```

### M-Lab Broadband Usage in Texas

```{r M-Lab Broadband Usage, echo=FALSE, cache=TRUE}
## M-Lab Broadband Map ##
map %>% addTiles() %>% setView(lng = -100.000, lat = 31.000, zoom = 6) %>% 
  addPolygons(stroke = F, smoothFactor = 0.2, fillOpacity = 0.9,
              color = ~pal(pct_broadband_mlab),
              popup = ~popup_tx) %>% 
  addLegend("bottomright", pal = pal, values = ~pct_broadband_mlab,
            title = "M-Lab Broadband (%)",
            labFormat = labelFormat(suffix = "%", transform = function(x) 100*x), na.label = "N/A", opacity = 1)
```


