---
title: "Coarsened Exact Matching (CEM) Analysis"
author: "Jaewon R. Choi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = F, error = F)
```

In this document, I'll go through the process of **Coarsened Exact Matching (CEM)**, which allows us to only include comparable counties in the dataset we have been working on. Through this process, we can minimize the imbalance in covariates, which can be problematic for the full regression model.

## Coarsened Exact Matching (CEM)

To conduct CEM in R, we will use `cem` package. The method and the package have been developed and advanced by a team of researchers. You can find more details [here](https://gking.harvard.edu/cem).

```{r import packages, results='hide'}
set.seed(5000)
# install.packages("cem")
library(tidyverse)
library(cem)
library(ggplot2)

```

Clean the worksapce and import raw dataset from GitHub repository.

```{r import dataset, results='hide'}
#rm(list = ls())     # Clean workspace

d <- read_csv("https://raw.githubusercontent.com/texastipi/broadband_entrepreneurship/master/Broadband-Entrepreneurship-TXKSME.csv")
glimpse(d)
```

### Treatment, Outcome, and Covariate Variables

CEM involves defining treatment, outcome, and covariate variables of interest. In our analysis, we are interested in the treatment effect of broadband-related variables on entrepreneurial outcome variables. The reason for conducting CEM is to address the imbalance in terms of various economic and demographic factors of different counties. Below are the treatment, outcome, and covariates. 


#### Treatment

For the listed treatment braodband variables, we split each variable into two categories (Low, High). [Gallardo, Whitacre, Kumar, & Upendram (2021)](https://ideas.repec.org/a/spr/anresc/v66y2021i1d10.1007_s00168-020-01015-0.html) used three categories and eliminated the 'Medium' category and consider 'High' as the treated group and 'Low' as untreated group. However, our sample is substantially smaller and we are more likely to end up with matched observations that are too small for any inferential statistical analysis considering the number of pre-treatment covariates. Therefore, we will convert the following variables to mean-based treatment categories:

* `pct_25_3_dec_2019_fcc`: FCC 477 availability of broadband at 25/3Mbps per county (%, data as of Dec 2019)
* `pct_100_10_dec_2019_fcc`: FCC 477 availability of broadband at 100/10Mbps per county (%, data as of Dec 2019)
* `pct_250_25_dec_2019_fcc`: FCC 477 availability of broadband at 250/25Mbps per county (%, data as of Dec 2019)
* `pct_1000_100_dec_2019_fcc`: FCC 477 availability of broadband at 1000/100Mbps per county (%, data as of Dec 2019)
* `pct_fixed_acs_2019`: Fixed broadband service subscription according to ACS 5-year estimates (%, 2019)
* `pct_bb_qos`: Compostive broadband quality of service (QoS) measure based on Microsoft's broadband through-put data (2020) and Mlab's broadband test data (2018-2019) (%)


#### Outcome

For the entrepreneurial outcome variables, we investigate several measures of entrepreneurship that were used in the traditional multiple regression analysis. In addition, we explore non-farm proprietorship per capita as a new possible representation of entrepreneurship in a county.

* `pct_nonfarm_bea_2019`: Share of non-farm proprietors over total employment of a county (%, 2019; Source: BEA)
* `vd_mean_20`: Average venture density (2020; Source: GoDaddy)
* `havd_mean_20`: Average highly active venture density (2020; Source: GoDaddy)
* `nonfarmprop_percapita`: Number of non-farm proprietors per capita (2019; Source: BEA)


#### Covariates

For covariates, we include several economic and demographic variables that could be closely related to the imbalance within the sample. To give an example, Gallardo et al. (2021) used natural log of population, % of people with bachelor's degree, unemployment rate, and industry diversity index. Our full regression models used industry characteristics, education, age, and rurality as control variables. Here, we will use log of population, % of people with bachelor's degree, unemployment rate, industry diversity index as covariates for matching. Rurality measures will be investigated in relation to the broadband treatments in the following  regression models.

* Log of `population_2019`: Natural log of county population (2019)
* `indstry_diversity`: Industry diversty index calculated based on methods described by Gallardo et al. (2021)
* `pctbachelors_2019`: % of people with Bachelor's degree (2019; Source: ACS 5-year estimates)
* `pct_unemployment_2019`: Unemployment rate (2019; Source: ACS 5-year estimates)

#### Rurality measures as additional independent variable

* `RUCC_2013`: Rural-Urban Continuum Codes developed by [USDA (2013)](https://www.ers.usda.gov/data-products/rural-urban-continuum-codes.aspx)
* `metro_f`: Metro/Non-Metro categories based on the RUCC documentation
* `IRR2010`: Rurality index created by [Waldorf & Kim (2019)](https://purr.purdue.edu/publications/2960/1). Continuous measure ranging from 0 to 1


### Data Preparation and Matching

Let's first create a subset of data with only the variables we need and some basic identities.

```{r subset data}
## Subset data with the aforementioned variables, create NLpop_2019 (natural log of population)

d2 <- d %>% select(county_FIPS, county.x,
                   pct25_3_dec_2019_fcc, pct100_10_dec_2019_fcc, pct250_25_dec_2019_fcc, pct1000_100_dec_2019_fcc,
                   pct_fixed_acs_2019, pct_bb_qos,
                   pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                   population_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, RUCC_2013, metro_f, IRR2010) %>% 
  mutate(LNpop_2019 = log(population_2019))

```

Let's create treatment variables by recoding the original variables. First, we'll take a look at the variables distribution and create categories. For matching to work and be useful in the final analysis, we create categories based on average. 

```{r create treatment variable}
## Take a look at the broadband variable summaries

d2 %>% select(pct25_3_dec_2019_fcc, pct100_10_dec_2019_fcc, pct250_25_dec_2019_fcc, pct1000_100_dec_2019_fcc,
             pct_fixed_acs_2019, pct_bb_qos) %>% summary()

## Use first and third quartile for creating categories
## For the 1000/100 Mbps measure, the 1st quartile is 0. Therefore, we will use mean split as an alternative

d2 <- d2 %>% 
  mutate(BB_25_3_high = case_when(pct25_3_dec_2019_fcc < mean(pct25_3_dec_2019_fcc, na.rm = T) ~ 0,
                                  pct25_3_dec_2019_fcc > mean(pct25_3_dec_2019_fcc, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_),
         BB_100_10_high = case_when(pct100_10_dec_2019_fcc < mean(pct100_10_dec_2019_fcc, na.rm = T) ~ 0,
                                  pct100_10_dec_2019_fcc > mean(pct100_10_dec_2019_fcc, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_),
         BB_250_25_high = case_when(pct250_25_dec_2019_fcc < mean(pct250_25_dec_2019_fcc, na.rm = T) ~ 0,
                                  pct250_25_dec_2019_fcc > mean(pct250_25_dec_2019_fcc, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_),
         BB_1000_100_high = case_when(pct1000_100_dec_2019_fcc < mean(pct1000_100_dec_2019_fcc, na.rm = T) ~ 0,
                                  pct1000_100_dec_2019_fcc > mean(pct1000_100_dec_2019_fcc, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_),
         BB_adoption_high = case_when(pct_fixed_acs_2019 < mean(pct_fixed_acs_2019, na.rm = T) ~ 0,
                                  pct_fixed_acs_2019 > mean(pct_fixed_acs_2019, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_),
         BB_qos_high = case_when(pct_bb_qos < mean(pct_bb_qos, na.rm = T) ~ 0,
                                  pct_bb_qos > mean(pct_bb_qos, na.rm = T) ~ 1,
                                  TRUE ~ NA_real_))

str(d2)

```

We'll now use `cem` package to match the sample to treatment based on the covariates we mentioned above.

Note that the package does not allow `NA`s in the treatment variable. Therefore, we have to create separate datasets for each treatment variable of interest.

Also, our sample size after omiting `NA`s will become substantially small. Especially as we are using 4 pre-treatment covariates for matching. This could be problematic, making the following regression analyses less effective and meaningful. Therefore, we will apply user choiced coarsening to the covariates. This will relax the categories for matching. Specifically, we will set custom cut points for each covariate by retrieving break points for 3 bins in the total range of each variable.

```{r CEM matching}
## Inspect how much observations are there in treated and control groups
table(d2$BB_25_3_high)
table(d2$BB_100_10_high)
table(d2$BB_250_25_high)
table(d2$BB_1000_100_high)
table(d2$BB_adoption_high)
table(d2$BB_qos_high)

## Set cut points for each covariate
popcut <- hist(d2$LNpop_2019, br=seq(min(d2$LNpop_2019, na.rm = T), max(d2$LNpop_2019, na.rm = T), length.out = 5), plot = F)$breaks

indstrycut <- hist(d2$indstry_diversity, br=seq(min(d2$indstry_diversity), max(d2$indstry_diversity), length.out = 5), plot = F)$breaks

educut <- hist(d2$pctbachelors_2019, br=seq(min(d2$pctbachelors_2019), max(d2$pctbachelors_2019), length.out = 5), plot = F)$breaks

unempcut <- hist(d2$pct_unemployment_2019, br=seq(min(d2$pct_unemployment_2019), max(d2$pct_unemployment_2019), length.out = 5), plot = F)$breaks

# Ruralities
irrcut <- hist(d2$IRR2010, br = seq(min(d2$IRR2010), max(d2$IRR2010), length.out = 5), plot = F)$breaks


mycp <- list(LNpop_2019 = popcut, indstry_diversity = indstrycut, pctbachelors_2019 = educut, pct_unemployment_2019 = unempcut, IRR2010 = irrcut)

## List of covariates
vars <- c("LNpop_2019", "indstry_diversity", "pctbachelors_2019", "pct_unemployment_2019", "IRR2010")

droplst <- c("pct_nonfarm_bea_2019", "vd_mean_20", "havd_mean_20", "nonfarmprop_percapita", "metro_f")

#### Treatment: BB_25_3_high ####

d25_3 <- d2 %>% select(BB_25_3_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
d25_3 <- data.frame(na.omit(d25_3))

## Overall imbalance check

imbalance(group = d25_3$BB_25_3_high, data = d25_3[vars])

## CEM match using user-choice coarsening

match_fcc_25_3 <- cem(treatment = "BB_25_3_high", data = d25_3,
                      drop = droplst,
                      cutpoints = mycp, keep.all = T)

match_fcc_25_3

#### Treatment: BB_100_10_high ####

d100_10 <- d2 %>% select(BB_100_10_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
d100_10 <- data.frame(na.omit(d100_10))

## Overall imbalance check

imbalance(group = d100_10$BB_100_10_high, data = d100_10[vars])

## CEM match using user-choice coarsening

match_fcc_100_10 <- cem(treatment = "BB_100_10_high", data = d100_10,
                        drop = droplst,
                        cutpoints = mycp, keep.all = T)

match_fcc_100_10

#### Treatment: BB_250_25_high ####

d250_25 <- d2 %>% select(BB_250_25_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
d250_25 <- data.frame(na.omit(d250_25))

## Overall imbalance check

imbalance(group = d250_25$BB_250_25_high, data = d250_25[vars])

## CEM match using user-choice coarsening

match_fcc_250_25 <- cem(treatment = "BB_250_25_high", data = d250_25,
                        drop = droplst,
                        cutpoints = mycp, keep.all = T)

match_fcc_250_25

#### Treatment: BB_1000_100_high ####

d1000_100 <- d2 %>% select(BB_1000_100_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
d1000_100 <- data.frame(na.omit(d1000_100))

## Overall imbalance check

imbalance(group = d1000_100$BB_1000_100_high, data = d1000_100[vars])

## CEM match using user-choice coarsening

match_fcc_1000_100 <- cem(treatment = "BB_1000_100_high", data = d1000_100,
                        drop = droplst,
                        cutpoints = mycp, keep.all = T)

match_fcc_1000_100

#### Treatment: BB_adoption_high ####

dadoption <- d2 %>% select(BB_adoption_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
dadoption <- data.frame(na.omit(dadoption))

## Overall imbalance check

imbalance(group = dadoption$BB_adoption_high, data = dadoption[vars])

## CEM match using user-choice coarsening

match_fcc_adoption <- cem(treatment = "BB_adoption_high", data = dadoption,
                        drop = droplst,
                        cutpoints = mycp, keep.all = T)

match_fcc_adoption

#### Treatment: BB_qos_high ####

dqos <- d2 %>% select(BB_qos_high,
                    pct_nonfarm_bea_2019, vd_mean_20, havd_mean_20, nonfarmprop_percapita,
                    LNpop_2019, indstry_diversity, pctbachelors_2019, pct_unemployment_2019, IRR2010, metro_f)
dqos <- data.frame(na.omit(dqos))

## Overall imbalance check

imbalance(group = dqos$BB_qos_high, data = dqos[vars])

## CEM match using user-choice coarsening

match_fcc_qos <- cem(treatment = "BB_qos_high", data = dqos,
                        drop = droplst,
                        cutpoints = mycp, keep.all = T)

match_fcc_qos

```

### Causal Inference on the Matched Data

In this section, I will use linear model to estimate the sample average treatment effect on the treated (SATT) using weights produced by CEM stored in the matched dataset. Each subsection is laid out based on different broadband measures (i.e., treatment measures). There will be four models fitted for each treatment broadband variable. The model will estimate broadband treatment effect on the dependent variable. Additionally, the models estimate main effect of metro/non-metro classification and interaction effect as well. 

#### Broadband 25/3Mbps on Entrepreneurship measures

```{r causal inference analysis1}

#### Treatment: BB_25_3_high & Outcome: pct_nonfarm_bea_2019 ####

mod_25_3_nonfarm <- att(match_fcc_25_3, pct_nonfarm_bea_2019 ~ BB_25_3_high, data = d25_3)
summary(mod_25_3_nonfarm)

#### Treatment: BB_25_3_high & Outcome: vd_mean_20 ####

mod_25_3_vd <- att(match_fcc_25_3, vd_mean_20 ~ BB_25_3_high, data = d25_3)
summary(mod_25_3_vd)

#### Treatment: BB_25_3_high & Outcome: havd_mean_20 ####

mod_25_3_havd <- att(match_fcc_25_3, havd_mean_20 ~ BB_25_3_high, data = d25_3)
summary(mod_25_3_havd)

#### Treatment: BB_25_3_high & Outcome: nonfarmprop_percapita ####

mod_25_3_nonfarmpc <- att(match_fcc_25_3, nonfarmprop_percapita ~ BB_25_3_high, data = d25_3)
summary(mod_25_3_nonfarmpc)

```

#### Broadband 100/10Mbps on Entrepreneurship measures

```{r causal inference analysis2}

#### Treatment: BB_100_10_high & Outcome: pct_nonfarm_bea_2019 ####

mod_100_10_nonfarm <- att(match_fcc_100_10, pct_nonfarm_bea_2019 ~ BB_100_10_high, data = d100_10)
summary(mod_100_10_nonfarm)

#### Treatment: BB_100_10_high & Outcome: vd_mean_20 ####

mod_100_10_vd <- att(match_fcc_100_10, vd_mean_20 ~ BB_100_10_high, data = d100_10)
summary(mod_100_10_vd)

#### Treatment: BB_100_10_high & Outcome: havd_mean_20 ####

mod_100_10_havd <- att(match_fcc_100_10, havd_mean_20 ~ BB_100_10_high, data = d100_10)
summary(mod_100_10_havd)

#### Treatment: BB_100_10_high & Outcome: nonfarmprop_percapita ####

mod_100_10_nonfarmpc <- att(match_fcc_100_10, nonfarmprop_percapita ~ BB_100_10_high, data = d100_10)
summary(mod_100_10_nonfarmpc)

```

#### Broadband 250_25Mbps on Entrepreneurship measures

```{r causal inference analysis3}

#### Treatment: BB_250_25_high & Outcome: pct_nonfarm_bea_2019 ####

mod_250_25_nonfarm <- att(match_fcc_250_25, pct_nonfarm_bea_2019 ~ BB_250_25_high, data = d250_25)
summary(mod_250_25_nonfarm)

#### Treatment: BB_250_25_high & Outcome: vd_mean_20 ####

mod_250_25_vd <- att(match_fcc_250_25, vd_mean_20 ~ BB_250_25_high, data = d250_25)
summary(mod_250_25_vd)

#### Treatment: BB_100_10_high & Outcome: havd_mean_20 ####

mod_250_25_havd <- att(match_fcc_250_25, havd_mean_20 ~ BB_250_25_high, data = d250_25)
summary(mod_250_25_havd)

#### Treatment: BB_100_10_high & Outcome: nonfarmprop_percapita ####

mod_250_25_nonfarmpc <- att(match_fcc_250_25, nonfarmprop_percapita ~ BB_250_25_high, data = d250_25)
summary(mod_250_25_nonfarmpc)

```

#### Broadband 1000_100Mbps on Entrepreneurship measures

```{r causal inference analysis4}

#### Treatment: BB_1000_100_high & Outcome: pct_nonfarm_bea_2019 ####

mod_1000_100_nonfarm <- att(match_fcc_1000_100, pct_nonfarm_bea_2019 ~ BB_1000_100_high, data = d1000_100)
summary(mod_1000_100_nonfarm)

#### Treatment: BB_100_10_high & Outcome: vd_mean_20 ####

mod_1000_100_vd <- att(match_fcc_1000_100, vd_mean_20 ~ BB_1000_100_high, data = d1000_100)
summary(mod_1000_100_vd)

#### Treatment: BB_100_10_high & Outcome: havd_mean_20 ####

mod_1000_100_havd <- att(match_fcc_1000_100, havd_mean_20 ~ BB_1000_100_high, data = d1000_100)
summary(mod_1000_100_havd)

#### Treatment: BB_100_10_high & Outcome: nonfarmprop_percapita ####

mod_1000_100_nonfarmpc <- att(match_fcc_1000_100, nonfarmprop_percapita ~ BB_1000_100_high, data = d1000_100)
summary(mod_1000_100_nonfarmpc)

```

#### Broadband Adoption on Entrepreneurship measures

```{r causal inference analysis5}

#### Treatment: BB_100_10_high & Outcome: pct_nonfarm_bea_2019 ####

mod_adoption_nonfarm <- att(match_fcc_adoption, pct_nonfarm_bea_2019 ~ BB_adoption_high, data = dadoption)
summary(mod_adoption_nonfarm)

#### Treatment: BB_100_10_high & Outcome: vd_mean_20 ####

mod_adoption_vd <- att(match_fcc_adoption, vd_mean_20 ~ BB_adoption_high, data = dadoption)
summary(mod_adoption_vd)

#### Treatment: BB_100_10_high & Outcome: havd_mean_20 ####

mod_adoption_havd <- att(match_fcc_adoption, havd_mean_20 ~ BB_adoption_high, data = dadoption)
summary(mod_adoption_havd)

#### Treatment: BB_100_10_high & Outcome: nonfarmprop_percapita ####

mod_adoption_nonfarmpc <- att(match_fcc_adoption, nonfarmprop_percapita ~ BB_adoption_high, data = dadoption)
summary(mod_adoption_nonfarmpc)

```

#### Broadband Quality of Service on Entrepreneurship measures

```{r causal inference analysis6}

#### Treatment: BB_qos_high & Outcome: pct_nonfarm_bea_2019 ####

mod_qos_nonfarm <- att(match_fcc_qos, pct_nonfarm_bea_2019 ~ BB_qos_high, data = dqos)
summary(mod_qos_nonfarm)

#### Treatment: BB_qos_high & Outcome: vd_mean_20 ####

mod_qos_vd <- att(match_fcc_qos, vd_mean_20 ~ BB_qos_high, data = dqos)
summary(mod_qos_vd)

#### Treatment: BB_qos_high & Outcome: havd_mean_20 ####

mod_qos_havd <- att(match_fcc_qos, havd_mean_20 ~ BB_qos_high, data = dqos)
summary(mod_qos_havd)

#### Treatment: BB_qos_high & Outcome: nonfarmprop_percapita ####

mod_qos_nonfarmpc <- att(match_fcc_qos, nonfarmprop_percapita ~ BB_qos_high, data = dqos)
summary(mod_qos_nonfarmpc)

```

