---
title: "Linear Regression Analyses"
author: "Jaewon R. Choi"
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, message = FALSE, error = FALSE)
```

In this document, I will set up, run, and examine several multiple regression models. In general, the models investigate the relationships between **broadband** and **entrepreneurship**. Specifically, **how broadband influences entrepreneurship**. Furthermore, the models will explore how different measures of broadband, specifically measures of availability, adoption, and quality of service (QoS) explain entrepreneurial activities differently. Finally, I will explore how broadband interacts with rurality in its effect on entrepreneurial factors.

```{r Load packages & Get the dataset, results='hide', include=FALSE}

## Load packages
library(tidyverse)
library(ggplot2)
library(gridExtra)
#install.packages("stargazer", dependencies = T)    # A package for better looking tables for results
library(stargazer)
#install.packages("sjPlot")
library(sjPlot)
set.seed(5000)

## Read in dataset
tx_bb_entrepreneur_merged_v2 <- read_csv("https://raw.githubusercontent.com/texastipi/broadband_entrepreneurship/master/Broadband-Entrepreneurship-TXKSME.csv")

bb_entrepreneur_merged_all <- tx_bb_entrepreneur_merged_v2 %>% 
  mutate(chg_pct_50_est_cbp_2012_2018 = pct_50_est_cbp_2018 - pct_50_est_cbp_2012,
         chg_pct_10_est_cbp_2012_2018 = pct_10_est_cbp_2018 - pct_10_est_cbp_2012,
         chgn_nonemp_2012_2018 = neest_nemp_2018 - neest_nemp_2012)

tx_bb_entrepreneur_merged_v2 <- bb_entrepreneur_merged_all %>% 
  filter(ST == "TX")
ks_bb_entrepreneur_merged_v2 <- bb_entrepreneur_merged_all %>% 
  filter(ST == "KS")
me_bb_entrepreneur_merged_v2 <- bb_entrepreneur_merged_all %>% 
  filter(ST == "ME")

```

## Broadband and Entrepreneurship

First, let's take another look at some of the key variables.

### Entrepreneurship

* `IRR2010`: Rural index (larger = rural)
* **Entrepreneurship (2018)**
  + `pct_nonfarm_bea_2018`: % of nonfarm proprietors over total employment in 2018
  + `venturedensity_mean`: Average venture density in 2018 and 2019 (GoDaddy)
* **Change Factors (2012-2018)**
  + `pct_chg_bea_2012_2018`: Change in % of nonfarm proprietors b/w 2012 and 2018

>Nonfarm proprietors share is defined as the percentage of nonfarm proprietorships over total employment in the county in 2018. According to the Bureau of Economic Analysis (BEA), nonfarm proprietorship **"consists of the number of nonfarm sole proprietorships and the number of individual general partners in nonfarm partnerships."**. Change in the share of nonfarm proprietorship is a simple change measure calculated by substracting nonfarm proprietors share in 2012 from the same measure in 2018. 

### Broadband

* `pct_bb_fcc_2019`: FCC broadband availability in % (June 2019)
* `pct_broadband_MS`: MS broadband availability in % (2019)
* `pct_fixed_acs_2018`: ACS broadband subscription in % (2018)
* `pct_broadband_mlab`: M-Lab broadband measure (2019)

### Broadband's Effect on Entrepreneurial Outcome

Here I investigate **models that estimate broadband variables' effect on the entrepreneurial outcome.** Several different broadband measures are in the dataset. I will first model **each measure's relationship with the entrepreneurial outcome separately.**

Entrepreneurial outcomes can be represented by several variables in this dataset. As the ASU research team's white paper argued, the venture density provided by GoDaddy activities reflects actual entrepreneurial activities in the form of online domain creation. In the dataset, we also have Texas state's sole proprietor statistics. These variables reflect small and medium sized businesses in each county.

### Control Variables

For control variables, various demographic measures derived from the ACS estimates are available in the dataset. Furthermore, the rurality of the counties are reflected in the IRR index. Number of population, and regional industry characteristics will be also included as control variables.

***

# Texas

## Nonfarm Proprietors Share (2018)

* DV: Nonfarm Proprietor Share (2018)
* IV: FCC Broadband availability (2019), MS Broadband (2019), ACS Broadband Subscription (2018), M-Lab Broadband Usage (2019)
* Control: Rurality, Industry structure, Education, Age

```{r Nonfarm Proprietors Share, results='asis', echo=FALSE}
#### Model 1 ####

## DV: Nonfarm Proprietors Share
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_nonfarm_1 <- lm(pct_nonfarm_bea_2018 ~ pct_bb_fcc_2019 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_2 <- lm(pct_nonfarm_bea_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_3 <- lm(pct_nonfarm_bea_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_nonfarm_4 <- lm(pct_nonfarm_bea_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + pct_broadband_mlab + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_nonfarm_1, model_nonfarm_2, model_nonfarm_3, model_nonfarm_4, title = "Nonfarm Proprietors Share Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Nonfarm Proprietors Share (2018)"),
          covariate.labels = c("FCC Broadband Availability (%, 2019)","ACS Broadband Subscription (% of people with fixed broadband subscription)","MS Broadband (%, 2019)","M-Lab Broadband (% of testers with 25/3 Mbps speed)","Rurality Index (2010)","Agriculture (% of workers)","Construction (% of workers)","Wholesale (% of workers)","Retail (% of workers)","Transportation (% of workers)","IT (% of workers)","Finance (% of workers)","Professional (% of workers)","Education (% of workers)","Other occupation (% of workers)","Public (% of workers)","Education Less than Highschool","Bachelors Degree","Graduate Degree","Millenials","GenX","Babyboomer"), no.space = TRUE)

```

## Change in Nonfarm Proprietors Share (2012-2018)

* DV: Change in Nonfarm Proprietors Share (2012-2018)
* IV: FCC Broadband availability (2019), MS Broadband (2019), ACS Broadband Subscription (2018), M-Lab Broadband Usage (2019)
* Control: Rurality, Industry structure, Education, Age

```{r Change in Nonfarm Proprietors Share, results='asis', echo=FALSE}
#### Model 2 ####

## DV: Change in Nonfarm Proprietors Share
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_propchg_1 <- lm(pct_chg_bea_2012_2018 ~ pct_bb_fcc_2019 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_propchg_2 <- lm(pct_chg_bea_2012_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_propchg_3 <- lm(pct_chg_bea_2012_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_propchg_4 <- lm(pct_chg_bea_2012_2018 ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + pct_broadband_mlab + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_propchg_1, model_propchg_2, model_propchg_3, model_propchg_4, title = "Change in Nonfarm Proprietors Share Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Change in Nonfarm Proprietors Share (2012-2018)"),
          covariate.labels = c("FCC Broadband Availability (%, 2019)","ACS Broadband Subscription (% of people with fixed broadband subscription)","MS Broadband (%, 2019)","M-Lab Broadband (% of testers with 25/3 Mbps speed)","Rurality Index (2010)","Agriculture (% of workers)","Construction (% of workers)","Wholesale (% of workers)","Retail (% of workers)","Transportation (% of workers)","IT (% of workers)","Finance (% of workers)","Professional (% of workers)","Education (% of workers)","Other occupation (% of workers)","Public (% of workers)","Education Less than Highschool","Bachelors Degree","Graduate Degree","Millenials","GenX","Babyboomer"), no.space = TRUE)
```

## Venture Density

* DV: Venture Density (average over the period 2018-2019)
* IV: FCC Broadband availability (2019), MS Broadband (2019), ACS Broadband Subscription (2018), M-Lab Broadband Usage (2019)
* Control: Rurality, Industry structure, Education, Age

```{r Venture Density, results='asis', echo=FALSE}
#### Model 4 ####

## DV: Venture density
## IV: Broadband Availability (FCC) -> MS -> ACS -> M-lab

model_vd_1 <- lm(venturedensity_mean ~ pct_bb_fcc_2019 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2 <- lm(venturedensity_mean ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_3 <- lm(venturedensity_mean ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_4 <- lm(venturedensity_mean ~ pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + pct_broadband_mlab + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_vd_1, model_vd_2, model_vd_3, model_vd_4, title = "Venture Density Regression Results", type = "html",
          align = TRUE, dep.var.labels = c("Venture Density (2018-2019)"),
          covariate.labels = c("FCC Broadband Availability (%, 2019)","ACS Broadband Subscription (% of people with fixed broadband subscription)","MS Broadband (%, 2019)","M-Lab Broadband (% of testers with 25/3 Mbps speed)","Rurality Index (2010)","Agriculture (% of workers)","Construction (% of workers)","Wholesale (% of workers)","Retail (% of workers)","Transportation (% of workers)","IT (% of workers)","Finance (% of workers)","Professional (% of workers)","Education (% of workers)","Other occupation (% of workers)","Public (% of workers)","Education Less than Highschool","Bachelors Degree","Graduate Degree","Millenials","GenX","Babyboomer"), no.space = TRUE)

```

### Models with Proprietor/Nonemp as IV

Below, I explore regression models that consider **proprietors share as independent variables** representing overall industry characteristics of the county. Dependent variables are **venture density** measures as representations of entrepreneurial activities online.

* DV: Venture Density (2018-2019)
* IV: Nonfarm Proprietor Share (2018), FCC Broadband availability (2019), MS Broadband (2019), ACS Broadband Subscription (2018), M-Lab Broadband Usage (2019)
* Control: Rurality, Education, Age

```{r Venture Density and Proprietor as IV, results='asis', echo=FALSE}

model_vd_2.1 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.2 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + pct_bb_fcc_2019 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.3 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + pct_bb_fcc_2019 + pct_fixed_acs_2018 + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

model_vd_2.4 <- lm(venturedensity_mean ~ pct_nonfarm_bea_2018 + pct_bb_fcc_2019 + pct_fixed_acs_2018 + pct_broadband_MS + pct_broadband_mlab + IRR2010 + pctagriculture_2019 + pctconstruction_2019 + pctwholesale_2019 + pctretail_2019 + pcttransportation_2019 + pctinformation_2019 + pctfinance_2019 + pctprofessional_2019 + pctedu_healthcare_social_2019 + pctother_occupation_2019 + pctpublic_admin_2019 + pctlessthanhigh_2019 + pctbachelors_2019 + pctgraduate_2019 + pctmilennial_2019 + pctgenx_2019 + pctboomers_2019,
              data = tx_bb_entrepreneur_merged_v2)

## Generate Table
stargazer(model_vd_2.1, model_vd_2.2, model_vd_2.3, model_vd_2.4, type = "html", align = T,
          dep.var.labels = c("Venture Density (2018-2019)"),
          covariate.labels = c("Nonfarm Proprietor (%, 2018)",
                               "FCC Broadband Availability (%, 2017)",
                               "ACS Broadband Subscription (% of people with fixed broadband subscription)",
                               "MS Broadband (%, 2019)",
                               "M-Lab Broadband Use (% of testers with 25/3 Mbps speed)",
                               "Rurality Index (2010)",
                               "Agriculture (% of workers)",
                               "Construction (% of workers)",
                               "Wholesale (% of workers)",
                               "Retail (% of workers)",
                               "Transportation (% of workers)",
                               "IT (% of workers)",
                               "Finance (% of workers)",
                               "Professional (% of workers)",
                               "Education (% of workers)",
                               "Other occupation (% of workers)","Public (% of workers)","Education Less than Highschool","Bachelors Degree","Graduate Degree","Millenials","GenX","Babyboomer"),
          no.space = T)


```


